### 2022-09-28 Thesis/text/diskussion.tex
..

The implemented behaviors are a first step to increasing autonomy, but the behavior planner needs to create many more behaviors and fallbacks. Some behaviors not implemented in this thesis incorporate the Intel RSS rules for autonomous driving, like keeping appropriate distances, right-of-way rules, and adaptable speed based on occlusions.
Another area of future work is the creation of dedicated behaviors for multi-robot systems. E.g., sharing sensor data with other robots to overcome complete sensor failures or intelligent path planning to avoid collisions when robots can access the planned paths of other robots. 
Also, more work is needed to define a robot's safe state or position after triggering an emergency stop. Reaching these minimum risk states after emergencies is then the duty of the behavior planner.

>>>>

The implemented behaviors were a first step to increasing autonomy, but the behavior planner needs more behaviors and fallbacks. Some behaviors that are not implemented in this thesis incorporate the Intel RSS rules for autonomous driving, like keeping appropriate distances, right-of-way rules, and adaptable speed based on occlusions.
Another area of future work is the creation of dedicated behaviors for multi-robot systems. For example the sharing sensor data with other robots to overcome complete sensor failures or intelligent path planning to avoid collisions when robots can access the planned paths of other robots. 
Also, more work is needed to define a robot's safe state or position after triggering an emergency stop. Reaching these minimum risk states after emergencies is then the duty of the behavior planner.

### 2022-09-28 Thesis/text/ergebnisse.tex
..

Nevertheless, there is a lack of intelligence and autonomy when the robot stands still. A collision is forced, but the implemented behavior relies on the same mechanism as during the driving scenario. The missing differentiation led to a test case where the robot reversed into a wall because it was turned 90 degrees by the collision. That test failed because a human operator would be needed to correct the robot. This lack of robustness was not apparent in the driving collision scenario because the robot's force was insufficient to cause a significant shift in orientation when colliding with obstacles.

@@

The architectural design choices meet all the non-functional requirements. Implementing the whole behavior planning and system supervision system eliminates a single point of failure for the system. Even when the Navigation2 system collapses, is the robot able to move to a degree and, more importantly, stop completely (compare table \ref{tab:nonfn_req}, non$\_$fn$\_$req). The behavior tree and algorithms implemented in the behavior tree are all deterministic (non$\_$fn$\_$req3). The robots' behavior goes beyond pure reactivity when navigating through environments, as the advanced behaviors use a dedicated planning phase before the actions are carried out (non$\_$fn$\_$req4).

>>>>

Nevertheless, there is a lack of intelligence and autonomy when the robot stands still. A collision is forced, but the implemented behavior relies on the same mechanism as during the driving scenario. The missing differentiation led to a test case where the robot reversed into a wall because it was turned 90 degrees by the collision. Therefore, the test failed because a human operator would be needed to correct the robots position. This lack of robustness was not apparent in the driving collision scenario because the robot's force was insufficient to cause a significant shift in orientation when colliding with obstacles.

@@

The architectural design choices meet all the non-functional requirements. Implementing the behavior planning and system supervision system eliminates a single point of failure for the system. Even when the Navigation2 system collapses, the robot is able to move to a degree and, more importantly, stop completely (compare table \ref{tab:nonfn_req}, non$\_$fn$\_$req). The behavior tree and algorithms implemented in the behavior tree are all deterministic (non$\_$fn$\_$req3). The robots' behavior goes beyond pure reactivity when navigating through environments, as the advanced behaviors use a dedicated planning phase before the actions are carried out (non$\_$fn$\_$req4).
